Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-09-07 5_results_discussions/results_discussions.tex
no message

%% datasets

\section{Discussions}
\label{sec:discussions}
When the evaluation of the stages for \textit{Loan Application Process} and \textit{Environmental Permit Application Process} datasets are gathered together, the following results can be expressed:

>>>>

\input{5_results_discussions/loan-application-process/loan-application-process.tex}
\input{5_results_discussions/coselog-wabo/coselog-wabo.tex}

\subsection{Discussions}
\label{subsec:discussions}
When the evaluation of the stages for \textit{Loan Application Process} and \textit{Environmental Permit Application Process} datasets are gathered together, the following results can be expressed:
